divan: An R Shiny app for exploratory functional diversity analyses

### 2023-11-02 paper/paper.Rmd
yml update

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
author:
  - name: Facundo X. Palacio
    affiliation: '1, 2'
    corresponding: true
  - name: Caio Graco-Roza
    affiliation: '3'
  - name: Emma J. Hudgins
    affiliation: '4'
affiliation:
  - name: Sección Ornitología, Universidad Nacional de La Plata, B1900FWA La Plata, Argentina
    index: 1
  - name: Consejo Nacional de Investigaciones Científicas y Técnicas, La Plata, Argentina
    index: 2
  - name: University of Helsinki, Helsinki, Finland
    index: 3
  - name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne, Parkvile 3010 VIC, Australia
    index: 4
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: bibliography.bib
output: distill::distill_article
---

>>>>

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
author:
  - name: Facundo X. Palacio
    affiliation: '1, 2'
    corresponding: true
  - name: Caio Graco-Roza
    affiliation: '3'
  - name: Emma J. Hudgins
    affiliation: '4'
affiliation:
  - name: Sección Ornitología, Universidad Nacional de La Plata, B1900FWA La Plata, Argentina
    index: 1
  - name: Consejo Nacional de Investigaciones Científicas y Técnicas, La Plata, Argentina
    index: 2
  - name: University of Helsinki, Helsinki, Finland
    index: 3
  - name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne, Parkvile 3010 VIC, Australia
    index: 4
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: bibliography.bib
output: md_document
---
